Optimal (Multiway) Spatial Joins

### 2024-05-24 msj.tex
yufei

\extraspacing {\bf Generating $\bm{\J^*}$.} Take an arbitrary $(k-2)$-tuple $\bm{t} = (r'_1, r'_2, ...,$ $r'_{k-2}) \in \J(R_1', R'_2, ..., R'_{k-2})$. The reader should recall from Section~\ref{sec:bricks} that
\myitems{
    \item $B_\bm{t}$ is $\bigcap_{i=1}^{k-2} \bm{t}[i]$, i.e., the intersection of $r'_1, r'_2, ..., r'_{k-2}$;
    \item $\gleft(\bm{t})$ is the $r'_i$ ($1 \le i \le k-2$) with $\xleft(r'_i) = \xleft(B_\bm{t})$;
    \item $\gbot(\bm{t})$ is the $r'_i$ ($1 \le i \le k-2$) with $\ybot(r'_i) = \ybot(B_\bm{t})$.
}
We now introduce:
% \myitems{
%     \item $\cross(r_a, B; H)$, the set of segments in $H$ that cross $r_a$ and $B$;
%     \item $\cross(r_b, B; V)$, the set of segments in $V$ that cross $r_b$ and $B$.
% }
\myeqn{
    \dcross_H(\bm{t}) = \set{h \in H \mid \text{$h$ crosses both $B_\bm{t}$ and $\gleft(\bm{t})$}} \label{eqn:dcross-H} \\
    \dcross_V(\bm{t}) = \set{h \in H \mid \text{$v$ crosses both $B_\bm{t}$ and $\gbot(\bm{t})$}}. \label{eqn:dcross-H} 
}
The prefix ``d-'' stands for double. These sets have important properties as stated in the next lemma, whose proof can be found in Appendix~\ref{app:hv}:

@@

The rest of the section will focus on explaining how to prepare the sets $\dcross_H(\bm{t})$ of all $\bm{t} \in \J(R_1', ..., R_{k-2}')$ in $O(n \log n + k \cdot \out)$ time. An analogous algorithm can be used to compute the sets $\dcross_V(\bm{t})$ of all $\bm{t}$ in the same time complexity.

@@

Now construct from $R_i'$ a new set of rectangles: 
\myeqn{
    R^*_i = \set{r^* \mid r' \in R_i' \text{ and its top-sliced rectangle $r^*$ exists}}. \label{eqn:hv:type1:R*}
}
In Appendix~\ref{app:hv}, we show how to compute produce $R^*_1, ..., R^*_{k-2}$ together in $O(n + k \cdot \out)$ total time.

>>>>

\extraspacing {\bf Generating $\bm{\J^*}$.} Take an arbitrary $(k-2)$-tuple $\bm{t} = (r'_1, r'_2, ...,$ $r'_{k-2}) \in \J(R_1', R'_2, ..., R'_{k-2})$. The reader should recall from Section~\ref{sec:bricks} that
\myitems{
    \item $B_\bm{t}$ is $\bigcap_{i=1}^{k-2} \bm{t}[i]$, i.e., the intersection of $r'_1, r'_2, ..., r'_{k-2}$;
    \item $\gleft(\bm{t})$ is the $r'_i$ ($1 \le i \le k-2$) with $\xleft(r'_i) = \xleft(B_\bm{t})$;
    \item $\gbot(\bm{t})$ is the $r'_i$ ($1 \le i \le k-2$) with $\ybot(r'_i) = \ybot(B_\bm{t})$.
}
We now introduce:
% \myitems{
%     \item $\cross(r_a, B; H)$, the set of segments in $H$ that cross $r_a$ and $B$;
%     \item $\cross(r_b, B; V)$, the set of segments in $V$ that cross $r_b$ and $B$.
% }
\myeqn{
    \dcross_H(\bm{t}) = \set{h \in H \mid \text{$h$ crosses both $B_\bm{t}$ and $\gleft(\bm{t})$}} \label{eqn:dcross-H} \\
    \dcross_V(\bm{t}) = \set{h \in H \mid \text{$v$ crosses both $B_\bm{t}$ and $\gbot(\bm{t})$}}. \nn
    %\label{eqn:dcross-H} 
}
The prefix ``d-'' stands for double. These sets have important properties as stated in the next lemma, whose proof can be found in Appendix~\ref{app:hv}:

@@

The rest of the section will focus on how to prepare the sets $\dcross_H(\bm{t})$ of all $\bm{t} \in \J(R_1', ..., R_{k-2}')$ in $O(n \log n + k \cdot \out)$ time. An analogous method can be used to compute the sets $\dcross_V(\bm{t})$ of all $\bm{t}$ in the same time complexity.

@@

Next, we construct from $R_i'$ a new set of rectangles: 
\myeqn{
    R^*_i = \set{r^* \mid r' \in R_i' \text{ and its top-sliced rectangle $r^*$ exists}}. \label{eqn:hv:type1:R*}
}
In Appendix~\ref{app:hv}, we show how to compute produce $R^*_1, ..., R^*_{k-2}$ together in $O(n + k \cdot \out)$ total time.

Now, we compute $\cross_H(r^*)$ for each $r^* \in R^*_i$

\extraspacing {\bf Computing the ``d-cross'' Sets.}
